---
title: "QCB Structure and Drug ANOVA"
output: html_notebook
---

```{r}

if(!require(dplyr)){install.packages("dplyr")}
if(!require(FSA)){install.packages("FSA")}
if(!require(car)){install.packages("car")}
if(!require(agricolae)){install.packages("agricolae")}
if(!require(multcomp)){install.packages("multcomp")}
if(!require(DescTools)){install.packages("DescTools")}
if(!require(lsmeans)){install.packages("lsmeans")}
if(!require(multcompView)){install.packages("multcompView")}
if(!require(Rmisc)){install.packages("Rmisc")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(pwr)){install.packages("pwr")}

```

Function to run anova and tukey and save results to csv
```{r}
Run1AnovaTukey <- function(df, x1, y1, group) {
  x = unlist(df[x1])
  y = unlist(df[y1])
  
  ## model on y as function of different x
  AOV <- aov(y ~ x, data = df)
  
  ## Tukey gives pairwise comparison of different x groups as measured by y
  tukeyres <- TukeyHSD(AOV, conf.level = 0.95)
  result <- as.data.frame(tukeyres$x)
  write.csv(result, paste(y1, group, '1anovatukey.csv', sep = '__'))
}
```

Function to run initial anova to see if there's overall difference between groups
```{r}
Run1Anova <- function(df, x1, y1, group){
  x = unlist(df[x1])
  y = unlist(df[y1])
  
  ## y as a function of x - see if difference in x affect y
  model <- lm(y ~ x, data = df)
  
  # gives pairwise comparison of x groups to reference group (first column)
  print(summary(model)) 
  AOV <- anova(model)
  print(AOV) # gives overall significance if there are differences based on x
  
}

```

Two Way Anova function to show if there's overall difference between x_1 and x_2 grouping
```{r}

Run2AnovaTukey <- function(df, x_1, x_2, y_1){
  x1 = unlist(df[x_1])
  x2 = unlist(df[x_2])
  y = unlist(df[y_1])
  AOV2 <- aov(y ~ x1 + x2, data = df)
  print(summary(AOV2))
  tukeyresult <- TukeyHSD(AOV2, conf.level=0.95)
  result1 <- as.data.frame(tukeyresult$x1)
  result2 <- as.data.frame(tukeyresult$x2)

  write.csv(result1, paste(y_1, x_1, '2anova.csv', sep = '__'))
  write.csv(result2, paste(y_1, x_2, '2anova.csv', sep = '__'))

}

```

Reading csv file to load df

```{r}
setwd("//allen/aics/microscopy/Winnie/QCB/Python Scripts/Drug datasets export")

df <- read.csv('dff.csv', sep = ",", header = TRUE, stringsAsFactors = F)
df
```

To get list of column names in df
```{r}
str(df) 

```

Fitting linear model. However no AICS-0 as control, so results are giving significance of each to beta-actin group (reference)

Following line will run an ANOVA across groups separated by "structure_name" based on "cell_volume" measurements
```{r}
Run1Anova(df, 'structure_name', 'cell_volume')

```

ANOVA across groups separated by "structure_name" based on "dna_volume" measurements on dna_volume

```{r}
Run1Anova(df, 'structure_name', 'dna_volume')
```

ANOVA across groups separated by "structure_name" based on "cell_to_dna_volume" measurements on dna_volume

```{r}
Run1Anova(df, 'structure_name', 'cell_to_dna_volume')
```

All cell_vol, dna_vol, and celltodna_vol show statistical significance...

Do post-hoc TukeyHSD across groups separated by "structure_name"
on all three parameters to find which pairing are stat. sign. and save the resulting csv's

```{r}
# directory to save resulting csv's to
setwd("C:/Users/winniel/Desktop/test")


for (feature in list('cell_volume', 'dna_volume', 'cell_to_dna_volume')) {
  Run1AnovaTukey(df, 'structure_name', feature, 'alldrugs')
  
}

```

Run Anova Tukey on just DMSO control group based on measurements in 'cell_volume', 'dna_volume', 'cell_to_dna_volume'
```{r}

DMSO.subset <- subset(df, df$drug_label == 'Vehicle')

for (feature in list('cell_volume', 'dna_volume', 'cell_to_dna_volume')) {
  Run1Anova(DMSO.subset, 'structure_name', feature)
}
```

ANOVA TUkey on DMSO - only cell to dna volume has stat. significance and need to be ran
```{r}
# Directory to save resulting csv's to 
setwd("C:/Users/winniel/Desktop/test")

for (feature in list('cell_to_dna_volume')) {
  Run1AnovaTukey(DMSO.subset, 'structure_name', feature, 'Vehicle')
}
```



Run 2 way ANOVA assuming interaction first between 2 factors.
Result shows interaction not significant, re-run ANOVA model based on independance between factors
```{r}
setwd("C:/Users/winniel/Desktop/test")
for (feature in list('cell_volume', 'dna_volume', 'cell_to_dna_volume')) {
  Run2AnovaTukey(df, 'structure_name', 'drug_label', feature)
}
```

No interaction of x1 and x2 under cell_volume, went back to do pairwise anova comparison 
based on no interaction (changed in method; y~ x1*x2 to y~ x1+x2)

```{r}
Run2AnovaTukey(df, 'structure_name', 'drug_label', 'cell_volume')
```


Need to separate each cell line and run 1 way anova with dunnett test (compare each drug to DMSO)


```{r}
# Directory to save results
setwd("C:/Users/winniel/Desktop/test")

structures <- unique(df$structure_name)

for (structure in structures){
  strucsubset <- subset(df, df$structure_name == structure)
  
  drugs = unique(strucsubset$drug_label)
  
  ## Set levels
  levels = c('Vehicle')

  for (i in 1:length(drugs)) {
    if (drugs[i] != 'Vehicle'){
      levels[length(levels)+1] = drugs[i]
    }
  }
  strucsubset$drug_label = ordered(strucsubset$drug_label, levels = levels)
  
  for (feature in list('cell_volume', 'dna_volume', 'cell_to_dna_volume')) {
    ## Dunnett's test

    duntest <- DunnettTest(unlist(strucsubset[feature]), unlist(strucsubset['drug_label']), conf.level = 0.95)
    Results <- as.data.frame(duntest$Vehicle)
    write.csv(Results, paste(toString(structure), feature, 'duntest.csv', sep='__'))
  }
}

```
Initial anova results on different structures per drug group 

```{r}
# directory to save results to
setwd("C:/Users/winniel/Desktop/test")

drugs <- unique(df$drug_label)

for (drug in drugs){
  drugsubset <- subset(df, df$drug_label == drug)
  
  for (feature in list('cell_volume', 'dna_volume', 'cell_to_dna_volume')){
    Run1Anova(drugsubset, 'structure_name', feature, drug)
    
  }
}
```

Run 1-way anova with post-hoc Tukey on different structures per drug group

```{r}
# directory to save results

setwd("C:/Users/winniel/Desktop/test")



for (drug in drugs){
  drugsubset <- subset(df, df$drug_label == drug)
  
  for (feature in list('cell_volume', 'dna_volume', 'cell_to_dna_volume')){
    Run1AnovaTukey(drugsubset, 'structure_name', feature, drug)
    
  }
}

```


